Eliminating prior-bias from sparse-projection tomographic reconstructions

### 2020-07-23 paper/response.tex

\section{Associate Editor comments}
(We have numbered the original review comments as AE-Cx, and italicized for clarity)

Two of the reviewers have raised some serious concerns about the paper, including one reviewer who opines that this work is not suited for publication in the transactions in its current form. While these concerns are sufficiently serious to merit a negative decision, I have decided to give the authors an opportunity to revise the manuscript so that they may address the constructive comments of the reviewers carefully and thoroughly followed by another round of review to assess the manuscript. In addition to the reviewer specific comments, please pay specific attention to the following:\\

\textcolor{blue}{\textbf{AE-C1.}\textit{ Overall organization of the paper to improve the exposition.}}

\textbf{Response:} 
We have now made the following significant changes in the organization of the paper:
The introduction has been modified and the stage set for outlining our contributions have been made.  We have replaced the earlier Figure 1 (which did not have longitudinal data) with a more appropriate figure (Fig.1). The unfamiliar terms ``unselective'' and ``selective'' prior have now been replaced by ``uniform'' prior and ``spatially varying'' prior to better communicate the property of the respective priors.
A new section  (Section 2) named ``Related Work'' has been included separately to contrast this work with the prevailing work in the literature. 
Details of the datasets have been moved to a separate section (Section 4) so the ground is properly set.
The two earlier sections: methods and results sections have now been split into the following 4 sections. This ensures better readability and emphasizes the cases where both uniform prior and spatially-varying prior are useful.
\begin{itemize}
 \item Section 6: Uniform prior-based reconstruction
 \item Section 7: Results: Reconstruction by uniform prior
 \item Section 8: Spatially varying prior-based reconstruction
 \item Section 9: Results: Reconstruction by spatially varying prior
   \end{itemize}
For greater clarity, we have now removed Schematic 1 (as suggested by R1) from the paper. We have  ensured that the rest of the paper can be followed without it. We have also moved the discussion on the earlier patch-based methods to supplementary material~\cite{supp_paper}. However, results not reported earlier prior to this submission using the uniform prior on 3D volumetric data continues to be present (as mentioned above) in Section 6 since it forms an important part of our story for this paper.\\

@@

\textcolor{blue}{\textbf{AE-C2.}\textit{ Highlight clearly the novelty of the presented work and provide accurate comparisons to relevant algorithms in the case when one has access to prior scans.}}

\textbf{Response:} We have now re-written the contributions section (Sec.3 of the main paper), that highlights the novelty of our work.  
As a response to the comparisons required,  in many cases, our methods are incomparable to previous algorithms because of the nature of the longitudinal study  We discuss this in the related work section. Further we reiterate that in our earlier manuscript version, we had compared our method with l1-regularized least squares (l1-ls) and FDK for 3D reconstructions. We had also compared (Fig.8) our method with many other iterative methods such as (ART, SART and SIRT) -- this set of comparisons was buried in a footnote, and perhaps not easily visible.
In addition to these, we now have included Table 3 to show a quantitative comparison of SSIM values of the reconstruction by various methods shown in Fig.8.  We also discuss compressed sensing (see AE-C3) results.
In addition, 
R3 has referred to ``Region-based iterative reconstruction of Structurally Changing Objects in CT''. This reference is now mentioned in our related work; although this paper is not directly applicable in longitudinal studies where object-priors `are' available, there is a reference in this paper to another paper which does make use of object-prior. We show how our work is superior in our response to R3 below (we include this in the supplementary material~\cite{supp_paper}). \\

@@

\textbf{Response:} Agreed. See response is \textcolor{blue}{\textbf{R1-C3}}.\\

\textcolor{blue}{\textbf{R1-C3:}\textit{ In CS, since you use cross-validation on a test image to select $\lambda_1$, it is necessary to tune this parameter until you reach a desired SSIM or root-mean-squared-error (RMSE). With CS priors, I would expect increasing $\lambda_1$ to also lead to smoother results.}}

\textbf{Response:} With respect to Figure. 10(c) of the submitted paper which corresponds to Fig.17(c) of the new version, we have now updated the reconstruction after tuning $\lambda_1$ to get the optimal result for l1-ls, as suggested by Reviewer 1. The optimal $\lambda_1$ was found to be 1.7.

In Sec.5 of our supplementary material~\cite{supp_paper}, we describe why the image in Fig.17(c) (Fig.10(c) of the old version) appears over-regularized by presenting reconstructions on 2D potato dataset for different number of views and optimally tuned $\lambda_1$ values.   \\

@@

\textbf{Case 2: Noise with 0 mean and SD = 1$\%$ of the mean of the measurements}
\begin{figure}[!h]
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/with_noise/weightsIm_fbp30.png}
\captionsetup{labelformat=empty}       
 \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/with_noise/weightsIm_sirt30.png}
\captionsetup{labelformat=empty}
        \caption{SIRT}
     \end{subfigure}
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/with_noise/weightsIm_sart30.png}
\captionsetup{labelformat=empty}
        \caption{SART}
     \end{subfigure}
    \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/with_noise/weightsIm_fbp_sirt30.png}
\captionsetup{labelformat=empty}
        \caption{FBP + SIRT}
    \end{subfigure}
    \quad
        \begin{subfigure}[b]{0.2\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/artefacts/with_noise/weightsIm_fbp_sart_sirt30.png}
\captionsetup{labelformat=empty}
        \caption{FBP + SART + SIRT}
     \end{subfigure}
      \caption{Weights images by various methods while reconstructing the test in Fig.~\ref{fig:object-prior_test_potato_A1} from 12 views in the presence of noise.}
\label{fig:weights_with_noise}
\end{figure}

\textcolor{blue}{\textbf{R1-C6:}\textit{ In results, the images are simply too big relative to the ROIs, which are tiny. It is very difficult to see the changes within the ROI. If the paper is printed, then there is no way to zoom into the images. It will be better if you could also present zoomed images of the ROI. Otherwise, you could present one full sized image and rest of the images could be only the ROI. }}

\textbf{Response:} While the zoomed-in RoI of Okra is in Figure 13 of the old manuscript (Fig.14 of the new manuscript), the zoomed-in RoI of the sprouts dataset has now been added in Fig. 16.  For other cases, large sized images are in the supplementary material~\cite{supp_paper}.\\

@@

\textcolor{blue}{\textbf{R1-C15:}\textit{ You are allowed to submit documents or media as supplementary material. Instead of posting them on a dropbox, you could submit them as supplementary material to the journal. You could also use supplementary material to add additional text or figures to reduce number of pages in main paper.}}

\textbf{Response:} Thank you for the suggestion. We have now submitted the supplementary material  on the publication portal. \\

\textcolor{blue}{\textbf{R1-C16:}\textit{ To save space and if you feel comfortable, you could move the section III (A) (1) on patch based techniques to supplementary since it is not a contribution of your paper.}}

\textbf{Response:} In order to save space and for greater clarity, we have now moved the discussion on patch-based techniques to supplementary material~\cite{supp_paper}.

@@

\textcolor{blue}{\textbf{R2-C4. }\textit{P2, L50, left panel: ``reconstruction-'' should be corrected to ``reconstruction -''}}

 \textbf{Response:} Accepted. This has been corrected.\\

\textcolor{blue}{\textbf{R2-C5.}\textit{P5, L10, left panel: ``Eq 6'' should be corrected to ``Eq. 6'' (same in P6, L54, right panel}}

 \textbf{Response:} Accepted. This has been corrected, and the equation has now been moved to  supplementary material~\cite{supp_paper} (Eq.2). \\

@@

\textcolor{blue}{\textit{This paper extends an existing algorithm for reconstructing longitudinal tomographic data with a reduced number of projections, by adding a weight map that determines how much to weigh a specific term in the cost function for each voxel of the reconstructed image. The authors give an explanation of the approach, and show results for both simulated and experimental data. Although the proposed approach seems mathematically sound, the paper itself has several significant issues that make it difficult to assess whether the approach actually improves on existing work. }}\\

\textcolor{blue}{\textbf{R3-C1:}\textit{ Most importantly, results are compared with only a single existing method that is specifically designed for low-angle tomography (compressed sensing), and the results of that method seem sub-optimal (at least, it does not match my experience with both applying such methods myself and published results of such methods). }}

\textbf{ Response:} The results of the (compared, CS) method are sub-optimal because of a significantly fewer number of views.  We show  (see R3-C7) that if we increase the number of views, CS actually does very well, as expected, and as mentioned by the reviewer.

We have compared our 2D reconstructions with many other iterative techniques such as SIRT, SART and ART, as seen in Fig. 12 (Figure.8). Earlier we had not included the SSIM values,  and these now appear in Tab. 3.  In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012} (please see Sec.~4 of our supplementary material~\cite{supp_paper}.)\\

@@

\textcolor{blue}{\textbf{R3-C2:}\textit{ Since no details are given about the method that is compared with (what function does in optimize?}}

\textbf{ Response:} In our submitted paper, we had compared our method to the the standard filtered back projection (written as FBP in Figure 1), and CS sensing using l1-ls (e.g. Line 33, Column 2, Page 4). The function optimized was given in Equation 8. We agree that we should have mentioned this earlier in the description, and this has been taken care of in the revised document.

Of the many other prior-based techniques, we have now discussed  below how we contrast with them in Sec.2 (`Related work'). In addition, we have now performed a 2D reconstruction to compare our method with~\cite{Lee2012}. In~\cite{Lee2012}, the new changes are directly detected in the measurement space by computing the difference between the measurements of the test and the corresponding simulated measurements of the template. This difference-volume is then reconstructed and then fused (added to) with the original high quality template.
However, in the above method, the sub-sampling artefacts present in the difference-volume gets carried over to the final reconstructed image. This can be seen in the visual results (and quantitative comparison) in Sec.~4 of our supplementary material~\cite{supp_paper}.\\

@@

\textcolor{blue}{\textbf{R3-C5:}\textit{ The comparisons with existing methods in the current manuscript are insufficient to support the conclusions made in the paper. My main concerns are: - The authors only compare with a single method specific to reconstructing tomographic images from a low number of projections (which they call compressed sensing). However, this topic is highly studied, and there are many methods available for this. The paper would be improved by including results from more methods, for example dictionary learning, total variation minimization, algebraic techniques (DART etcetera), or even simply SIRT with a nonnegativity constraint.}}

\textbf{Response:} This comment is similar to R3-C4. The main aim of our paper is the usage of an object-prior along with a weights map for reconstruction from highly undersampled projections in a longitudinal study. When the number of views is extremely small, then undersampling artifacts will affect any baseline method, be it SIRT, CS, ART or any other. However incorporation of object priors will significantly help to mitigate those artifacts.
In Fig.12 (Figure 8), we had earlier shown a visual comparison of 2D reconstructions of one of the datasets (potato) by all of the following methods: FBP, CS with DCT as sparsity prior, CS with Haar as sparsity prior, ART, SART, SIRT and our weighted prior method.
We have now also included a quantitative comparison of the accuracy of these results in Tab. 3 of the new manuscript.\\

\textcolor{blue}{\textbf{R3-C6:}\textit{ No details are given about the CS method that was compared with. What type of sparsity did the method assume? What objective function did it minimize? What parameters did the authors choose? How were those parameters chosen? How many iterations were used to minimize the objective function? Without this information, the comparison does not have much information, and therefore can't be used to support the conclusions made in the paper.}}

\textbf{Response:} This is similar to R3-C3. We had earlier mentioned that we are using DCT in Page 6 (right column, line 58). For greater clarity, we have now mentioned this in Section 1 (Introduction, below Eq.1).
The objective function minimized while using l1-ls (CS) optimization is now introduced in Eq.1. This is the same as Eq. 6,  with $\lambda_2 = 0$.
Details of parameter selection is now in Section 9-B.
In our earlier submission, $\lambda_1$ and $\lambda_2$ values were chosen by reconstructing the test volume by sweeping through a range of values and selecting the set of values that gave a reasonable visual quality. The same value (=1) was retained for all datasets. In the current version of the paper, we have now tuned $\lambda_1$ (as per R1's suggestions) to maximize SSIM of the whole reconstructed test volume for l1-ls reconstruction of each dataset. This value was retained for uniform and spatially-varying prior based reconstruction as well. $\lambda_2$ was chosen clairvoyantly,  i.e., based on the value that gave the best visual results on the test.\\

@@

\textcolor{blue}{\textbf{R3-C7:}\textit{ Based on my experience with reconstructing tomographic data from few projections, I would expect the CS results to look \_much\_ better than what is presented in the paper. As an example, in Fig 10, based on the results of the FDK algorithm, I would expect any reasonable iterative method with regularization (CS or otherwise) to produce fairly accurate results. I'm not sure what the cause of this is, because no details about the used CS method are given (see point above). Looking at the images (and other images from iterative methods given by the authors), it seems like the methods have not converged yet, but there could be other causes.}}

\textbf{Response:} The methods have indeed converged. Also mention that the perceived quality of reconstruction results using any technique can be quite subjective, and also dependent on the structure of the image as well as the number of projection views. In order to demonstrate this, we show the quality of reconstructions by CS for a varying number of views in Sec. 5 of our supplementary material~\cite{supp_paper}. In this paper, we are considering a very small number of views.  
What is the cause: When the number of views is large, the reconstruction using CS (l1-ls) is indeed good. However, when the number of views decreases, the reconstruction using CS (LASSO) is blurred, but with the benefit of suppressed artefacts that are otherwise present in FBP reconstruction. This is illustrated in Sec. 5 of our supplementary material~\cite{supp_paper}.      
For the 3D reconstructions shown in the updated paper, the $\lambda_1$ value is now chosen by performing l1-ls reconstructions for a wide range of values and then selecting the one that maximizes SSIM.
We also observe that the optimal $\lambda_1$ value is different for each set of views. Hence, an accurate selection of $\lambda_1$ for every dataset and for every set of views may be impractical depending on the application constraints.\\

@@

\textcolor{blue}{\textbf{R3-C10:}\textit{ Related to the previous point, this type of data seems well suited for data-driven techniques (e.g. deep learning) that have become very popular in recent years. Many papers exist that use deep learning for improving tomographic reconstruction from a low number of projections. It would be useful to include a comparison with a deep learning method, and, at the very least, discuss the possibility of using deep learning in this context.}}

\textbf{Response:} Deep learning techniques typically require large amounts of data. However, any given longitudinal study will allow for a very limited amount of data.. Moreover, there will be major generalization errors in deep learning based techniques for direct tomographic reconstruction, and in a clinical setting, we believe, current deep learning methods need to evolve further.\\

\textcolor{blue}{\textbf{R3-C11:}\textit{The discussion of hyperparameter sensitivity is not very detailed. It is important to show how reconstruction change when adjusting these paremeters (for example, what happens if $\lambda_1$ is set to 0?). In the current manuscript, the authors simply give a range of values that worked for them, but this is not very informative since it depends critically on the scaling of the data, which we don't know.}}

\textbf{Response:} The effect of the hyperparameter k on the weights-map and final reconstruction was earlier shown Figures. 17 and 18 (Fig. 20 and 21). These figures show that the selection of k decides the sensitivity to noise (false positives) in the weights-map. The range of k values deal with the extreme cases of very less amount of noise (Figure 17-a ,Fig. 20-a) upto high levels of false positives at the expense of not missing any true positive. (Figure. 17-l, Fig. 20-l).In our experiments, the object prior had a stronger impact on reconstructions than the sparsity prior. This is because the object prior was built using high quality previous scans.

\textbf{Reconstruction with $\lambda_1 =0$:} Here, below is a slice from the reconstructed potato volume when $\lambda_1$ is set to $0$, i.e., with no sparsity prior and with object prior alone.
\begin{figure}[!h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/cs_lambda_0/testIm_green}
%\captionsetup{labelformat=empty}
        \caption{FDK}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/cs_lambda_0/fdkIm_green.png}
%\captionsetup{labelformat=empty}
        \caption{l1-ls}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/cs_lambda_0/weightedPriorIm_green.png}
%\captionsetup{labelformat=empty}
        \caption{Uniform Prior}
     \end{subfigure}
     \caption{Example of a reconstruction with zero sparsity prior.}
     \label{fig:potato_cs_lambda_0}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}
\begin{table}[!h]
  \centering
  \caption{SSIM of reconstructions shown in Fig.~\ref{fig:potato_cs_lambda_0}}
\begin{tabular}{|l|l|l|}
\hline
 & \textbf{FDK} & \textbf{Spatially varying prior} \\ \hline
\textbf{Red RoI} & 0.94 & 0.85 \\ \hline
\textbf{Green RoI} & 0.92 & 0.90 \\ \hline
\textbf{Cyan RoI} & 0.88 & 0.94 \\ \hline
\end{tabular}
\end{table}\\

@@

\textcolor{blue}{\textbf{R3-C12:}\textit{ A discussion about computational costs (time, memory) should be included in the paper. Since most of the shown results are for quite small images, I'm worried that the approach might not scale well to the large image sizes that are common in high-resolution tomography.   }}

\textbf{Response:}While the reconstruction accuracy was measured in the (small) regions of new changes, all reconstructions were performed for the full object volume.

### 2020-07-23 paper/tci.tex
pre-final, added results with cs_lambda=0

In this paper, we present a technique that makes use of multiple
object priors, corresponding to high quality reconstructions of
similar objects across time. We use these priors to improve the
reconstruction of the test from largely undersampled measurements. In
particular, we define the regions of change between the test and the
eigenspace spanned by the previous high quality object priors in a
purely data driven manner. Very importantly, our technique clearly
differentiates between genuine structural changes and ``changes'' that
appear due to undersampling artefacts.  Besides this, since we use a
statistical model with multiple object priors, we avoid the problem of
selecting an appropriate single object prior
unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and
also make use of the additional information available in the multiple
priors.

@@

 \textbf{Okra:} This dataset is that of an Okra specimen consisting of its five
scans (Fig.~\ref{fig:object-prior_test_okra}). Prior to the first scan, two cuts were
drilled on the surface of the specimen. This was followed by four
scans, each after introducing one new cut. The specimen was kept in
the same position throughout the acquisitions.The measurements
consisted of real circular cone-beam projections from 450 views, each of size
336$\times$156. 
%In cases where such an
%alignment is not present, all the template volumes must be pre-aligned
%before computing the eigenspace. The test must be registered to the
%object-prior after its preliminary pilot reconstruction.

In our experiments, the first volume was assumed to be the test while
the rest were used to build the object-prior. The ground truth
consists of volumes of size 338$\times$338$\times$123 reconstructed
using the Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} from the
full set of 450 view projections.
\\
 %--------------------------------okra data-------------------------------
\begin{figure}[!h]  
    \begin{subfigure}[b]{0.176\linewidth}
        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/okra/test_marked.png}}
\captionsetup{labelformat=empty}
        \caption{}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/template1_marked.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/template2_marked.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/template3_marked.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/template4_marked.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
     \caption{Okra 3D dataset: One slice each from the each of the scanned volumes. The first one is used as the test while the rest are used to build the object-prior. Notice that in the regions marked in red and green boxes, while all slices have deformities, the test has none.}
\label{fig:object-prior_test_okra}
\end{figure}
%----------------------------------------------------

\textbf{Potato:} This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}). While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato. Measurements from each scan consisted of real circular cone-beam projections from 900 views, each of size 150$\times$150. %Further, this alignment can be refined following every update of the reconstructed test volume.

In our experiments, the first 3 volumes were used to build the object-prior and the
last volume was used as the test. The ground truth consists of volumes of size 150$\times$150$\times$100 reconstructed using FDK from the full set of 900 projection views. 
%---------------------------------------
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.235\linewidth}
        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
\captionsetup{labelformat=empty}
\caption{}
\label{fig:potato3D_test}
     \end{subfigure}
      \caption{Potato 3D dataset: One slice each from the previously scanned objects (the first three from left) and a slice from the test 
        volume (extreme right). Notice the appearance of the fourth
        hole in the test slice. }
\label{fig:object-prior_test_potato_A}
\end{figure}

%\subsection{Simulated measurements from real-life reconstructed volumes}
\textbf{Sprouts:} This 3D dataset, which was also obtained at ANU,
consists of six reconstructed volumes corresponding to six scans of an
in-vivo sprout specimen imaged at its various stages of growth
(Fig.~\ref{fig:object-prior_test_sprouts}).  In contrast to the
scientific experiment performed for the case of the okra and potato
where we introduced man-made defects, the changes here are purely the
work of nature.

In our experiments, the first 5 volumes were used to build the object-prior and the
last volume was used as the test. The ground truth consists of FDK reconstructed
volumes of size 130$\times$130$\times$130 from a set of 1800 view
projections. For the test, cone-beam projections were generated from
the test volume. \\
%-------------------------sprouts data

@@

\textbf{Liver:} %We have used this dataset
 %to illustrate an application
%where \textit{both} uniform and spatially-varying priors are
%useful.
This data was sourced from Tata Memorial Centre~\cite{tmh} in 
  Parel, Mumbai.  This is the national comprehensive centre for the
  prevention, treatment, education and research in cancer, and is
  recognized as one of the leading cancer centres in India. The dataset (Fig.~\ref{fig:RFA2_test_object-prior}) consists
of parallel beam measurements that are generated from 2D slices of the
organ (liver) acquired at different stages of a radio-frequency
ablation study. In such a procedure~\cite{Dong2015}, the physician
inserts a thin needle-like probe into the organ. Repeated CT scans of
the patient are acquired in order to track the movement of the
needle and to ensure that it is reaching the appropriate target
tumor. Once the needle hits the tumor, a high-frequency electric
current is passed through the tip of the probe and this burns the
malignant tumor (ablation). The aim of the scan at this ablation stage is to
reveal accurate details of the changes within.

>>>>

In this paper, we present a technique that makes use of multiple
object priors, corresponding to high quality reconstructions of
similar objects across time. We use these priors to improve the
reconstruction of the test from largely undersampled measurements. In
particular, we define the regions of change between the test and the
eigenspace spanned by the previous high quality object priors in a
purely data driven manner. Additionally, our technique differentiates
between genuine structural changes and ``changes'' that appear due to
undersampling artefacts (as seen in Sec.4 of our supplementary
material~\cite{supp_paper}).  Besides this, since we use a statistical
model with multiple object priors, we avoid the problem of selecting
an appropriate single object prior
unlike~\cite{PICCS,Pourmorteza2015,Lee2012,pirple,Marjolein2016} and
also make use of the additional information available in the multiple
priors. Our technique also has the advantage of not requiring any
expert-domain knowledge about the object being scanned.

@@

 \textbf{Okra:} This dataset is that of an Okra specimen consisting of its five
scans (Fig.~\ref{fig:object-prior_test_okra}). Prior to the first scan, two cuts were
drilled on the surface of the specimen. This was followed by four
scans, each after introducing one new cut. The specimen was kept in
the same position throughout the acquisitions.The measurements
consisted of real circular cone-beam projections from 450 views, each of size
336$\times$156. 
%In cases where such an
%alignment is not present, all the template volumes must be pre-aligned
%before computing the eigenspace. The test must be registered to the
%object-prior after its preliminary pilot reconstruction.
In our experiments, the first volume was assumed to be the test while
the rest were used to build the object-prior. The ground truth
consists of volumes of size 338$\times$338$\times$123 reconstructed
using the Feldkamp-Davis-Kress (FDK) algorithm~\cite{FDK} from the
full set of 450 view projections.
\\
 %--------------------------------okra data-------------------------------
\begin{figure}[!h]  
    \begin{subfigure}[b]{0.176\linewidth}
        \fcolorbox{white}{blue}{\includegraphics[width=\textwidth]{../images/okra/test_marked.png}}
\captionsetup{labelformat=empty}
        \caption{}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/template1_marked.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/template2_marked.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/template3_marked.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/template4_marked.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
     \caption{Okra 3D dataset: One slice each from the each of the scanned volumes. The first one is used as the test while the rest are used to build the object-prior. Notice that in the regions marked in red and green boxes, while all slices have deformities, the test has none.}
\label{fig:object-prior_test_okra}
\end{figure}
%----------------------------------------------------

\textbf{Potato:} This dataset consisted of four scans of the humble potato (Fig.~\ref{fig:object-prior_test_potato_A}). While the first scan was taken of the undistorted potato, subsequent scans were taken of the same specimen, each time after drilling a new hole halfway into the potato. Measurements from each scan consisted of real circular cone-beam projections from 900 views, each of size 150$\times$150. %Further, this alignment can be refined following every update of the reconstructed test volume.
In our experiments, the first 3 volumes were used to build the object-prior and the
last volume was used as the test. The ground truth consists of volumes of size 150$\times$150$\times$100 reconstructed using FDK from the full set of 900 projection views. 
%---------------------------------------
\begin{figure}[!h]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.235\linewidth}
        \fcolorbox{blue}{blue}{\includegraphics[width=\textwidth]{../images/potato/testIm_color.png}}
\captionsetup{labelformat=empty}
\caption{}
\label{fig:potato3D_test}
     \end{subfigure}
      \caption{Potato 3D dataset: One slice each from the previously scanned objects (the first three from left) and a slice from the test 
        volume (extreme right). Notice the appearance of the fourth
        hole in the test slice. }
\label{fig:object-prior_test_potato_A}
\end{figure}

%\subsection{Simulated measurements from real-life reconstructed volumes}
\textbf{Sprouts:} This 3D dataset, which was also obtained at ANU,
consists of six reconstructed volumes corresponding to six scans of an
in-vivo sprout specimen imaged at its various stages of growth
(Fig.~\ref{fig:object-prior_test_sprouts}).  In contrast to the
scientific experiment performed for the case of the okra and potato
where we introduced man-made defects, the changes here are purely the
work of nature. In our experiments, the first 5 volumes were used to build the object-prior and the
last volume was used as the test. The ground truth consists of FDK reconstructed
volumes of size 130$\times$130$\times$130 from a set of 1800 view
projections. For the test, cone-beam projections were generated from
the test volume. \\
%-------------------------sprouts data

@@

\textbf{Liver:} %We have used this dataset
 %to illustrate an application
%where \textit{both} uniform and spatially-varying priors are
%useful.
This data was sourced from Tata Memorial Centre~\cite{tmh} in Parel,
Mumbai.  This is the national comprehensive centre for the prevention,
treatment, education and research in cancer, and is recognized as one
of the leading cancer centres in India. The dataset
(Fig.~\ref{fig:RFA2_test_object-prior}) from this longitudinal medical
study consists of 8 scans taken at different stages of radio-frequency
ablation study of a liver. In such a procedure~\cite{Dong2015}, the
physician inserts a thin needle-like probe into the organ. Repeated CT
scans of the patient are acquired in order to track the movement of
the needle and to ensure that it is reaching the appropriate target
tumor. Once the needle hits the tumor, a high-frequency electric
current is passed through the tip of the probe and this burns the
malignant tumor (ablation). The aim of the scan at this ablation stage
is to reveal accurate details of the changes within.

In our experiments, we generate parallel beam measurements from 2D
slices from each of the 8 volumes. Note that all these 8 slices are
located at the \emph{same} index (slice number corresponding to the
same depth) within each of the respective volumes.  Observe (in
Fig.~\ref{fig:RFA2_test_object-prior}) that the needle is seen in all
of the first 7 slices and the effect of ablation is seen in the 8th
slice.
%In our experiments using this dataset, we demonstrate the usefulness of \textit{both} uniform prior and spatially varying prior. For the first case, we choose the first 6 slices to build the object prior and use slice 7 as the test. For the latter case, we choose the first 7 slices to build the object prior and use slice 8 as the test.
%--------------------------Results on TMH data--------------------------
%------------------RFA 2 data
\begin{figure}[h!]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template1.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 1}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template2.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 2}
    \end{subfigure}
     \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template3.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 3}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template4.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 4}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template5.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 5}
    \end{subfigure}
              \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template6_color.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 6}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/template7.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 7}
    \end{subfigure}
       \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/tmh/RFA2/colorTestIm_ablation.png}
%\captionsetup{labelformat=empty}       
 \caption{slice 8}
    \end{subfigure}     
     \caption{Radio-frequency ablation dataset: One of the slices (512$\times$512) from each of the 8 scan volumes of a longitudinal study dataset of the liver. Note that in volumes (a) through (g), the needle (shown in red in (f)) approaches the target tumor. (h) the organ after the ablation: this slice is displayed on a separate intensity scale to enable proper viewing of the region marked in green that shows the after-effects of ablating the tumor.} 
\label{fig:RFA2_test_object-prior}
\end{figure}
